Re-finding to support a Deep Web Question Answering System

### 2010-03-05 paper/semsearch10/content/results_futurework_conclusion.tex
Added the results images

@@

In addition, we cannot fully depend on the DBpedia categories, since the relevant data available in DBpedia store is insufficient to represent the real world queries belonging to all realms. [e.g. musical bands]. We are planning to define new categories from the deep web [or find out new sources to fill those \textit{weak} realms] in our ontology hierarchy.

%% I may have misstated the statistics that are unique/repeats
% need to clarify the statistics 
%% Add language about how we 
Researchers have stated 39, 57, and 63 percent of web queries are unique \cite{1277770,331405,621942}.  We believe that a large percentage of the stated unique queries are in-fact related and parameterizable, meaning, several subsets of unique queries may be all related and may be answered using a single QRM.  It is difficult to discover this property between queries.  Previous work suggest techniques to find related queries but it will take new efficient methods to discover parameterizable queries.

@@

MORE

>>>>

% Results: figure 1  
\begin{figure}[t]
\centering
\includegraphics[width=85mm]{screen_intro.eps}
\caption{Introductory screen}
\label{fig:screen_intro}
\end{figure}

Initially, the user enters a query of interest, much as one would ask a question. When the user submits the query, the query is broken down into constituent parts of who, what when, and where. From there, a relevant answer is produced to respond to the requested information.

% Results: figure 2  
\begin{figure}[t]
\centering
\includegraphics[width=85mm]{screen_result.eps}
\caption{Results screen}
\label{fig:screen_result}
\end{figure}

After typing in a query, the user is presented with two sections. First, the user is shown the query and how it was broken down during the form submission. Second, the user is presented with the relevant answer, the realm to which it belongs, and the sites in which the answer was found. If multiple answers are retrieved, they are sorted by relevance, with the most relevant answer displaying at the top of the list.

@@

We cannot rely on the DBpedia categories and the associated Wikipedia
pages to provide corpora for all our realms.  The DBpedia categories
and the associated Wikipedia documents are insufficient to
characterize the linguistic space of queries belonging to many
different realms.  Reasonable prior probabilities for the names of
musical groups within the category \emph{musical groups}, for example,
will be significantly different from what would be manufactured by
simply finding n-gram frequency within the related Wikipedia
documents. We are investigating methods to identify categories within
the deep web and to find new sources to construct \textit{weak} realms
in our ontology hierarchy.

%% I may have misstated the statistics that are unique/repeats
% need to clarify the statistics 
%% Add language about how we 
Researchers have stated that somewhere from 39 to 63 percent of web
queries are unique \cite{1277770,331405,621942}.  We believe that a
large percentage of the stated unique queries are in-fact related and
parameterizable, meaning, several subsets of unique queries may be all
related and may be answered using a single QRM.  It is difficult to
discover this property between queries.  Previous work suggest
techniques to find related queries but it will take new efficient
methods to discover parameterizable queries.

@@
